Included Summary (teaching-v1.0)

### 2020-12-14 experiment-1/analysis/preprocessor/included_summary.Rmd
update included_summary
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Export only included participants
data_analysis~.txt are used for data analysis.
```{r export-csv, echo = TRUE}
fwrite(dt_ioi[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = here("trimmed", "data_analysis_ioi.txt"), sep = ",")
fwrite(dt_kot[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = here("trimmed", "data_analysis_kot.txt"), sep = ",")
fwrite(dt_vel[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = here("trimmed", "data_analysis_vel.txt"), sep = ",")
fwrite(dt_vel_diff[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = here("trimmed", "data_analysis_vel_diff.txt"), sep = ",")
```

>>>>

### Export only included participants
data_analysis~.txt are used for data analysis.
```{r export-csv, echo = TRUE}
fwrite(dt_ioi[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = "./trimmed/data_analysis_ioi.txt", sep = ",")
fwrite(dt_kot[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = "./trimmed/data_analysis_kot.txt", sep = ",")
fwrite(dt_vel[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = "./trimmed/data_analysis_vel.txt", sep = ",")
fwrite(dt_vel_diff[SubNr != 1 & SubNr != 3 & SubNr != 8 & SubNr != 14 & SubNr != 16], file = "./trimmed/data_analysis_vel_diff.txt", sep = ",")
```
